Digital History in Finland, 1488-1828

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
print(p)
}
```

>>>>

### BOOKINFINLAND-DONE4 TODO:kielten viilaus, pätee myös BOOKINFINLAND-5. Nyt "other" kentästä pitäisi irrottaa relevantit. Nouseeko ranska esiin niin että sille kannattaisi laittaa oma analyysiviiva?

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
print(p)
}
```
These are intriguing graphs. Potentially they reveal the story of the development of the Academy in Turku in a very elegant manner. All disciplines suffer a dramatic decline after 1700, which is due to external causes (war, famine etc.). Philosophy (including logic and rhetoric) do not bounce back once the situation is normalised towards the middle of eighteenth century. Having been thriving in 17th-century philosophy is close to extinction as an academic subject by the second half of eighteenth century. It seems that natural science (and related fields) take over, especially when extended topic of medicine is included here. What is interesting about natural science is that the printing happens in several different languages (note also that the topics included in this category are perhaps more wide-ranging, which might play a part). Economy (and related fields) is a tremendous case in point that should be contrasted with religious/devotional literature towards the second half of eighteenth century. The reason for this is that Swedish is the predominant language (whereas the devotional literature is mainly in Finnish). Hebrew-Latin-Greek seem to do better than philosophy. Thus, perhaps there is a point in that book: Vain hyödynkö tähden?. Latin publishing of theology (and related fields) goes down as well. History does suprisingly well throughout the period.
